Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-02 paper/paper.tex
revised abstract again

\begin{abstract}
Full-waveform inversion is an adjoint-based optimization problem in seismic
imaging that processes terabytes of data and regularly exceeds the memory
capacity of available computers. A popular strategy to reduce the memory
requirement is data compression, which can reduce the memory
footprint by a certain factor. An alternative is
checkpointing, where data is stored at selected points in
time, and values at other times are recomputed as needed from the last stored state.
This allows arbitrarily large adjoint computations with limited memory, at the cost
of additional recomputations.

>>>>

\begin{abstract}
Full-waveform inversion is an adjoint-based optimization problem in seismic
imaging that processes terabytes of data, regularly exceeding the memory
capacity of available computers. Data compression is an effective strategy to
reduce this memory requirement by a certain factor, particularly if some loss in
accuracy is acceptable. A popular alternative is checkpointing, where data is
stored at selected points in time, and values at other times are recomputed as
needed from the last stored state.  This allows arbitrarily large adjoint
computations with limited memory, at the cost of additional recomputations.
